### 2015-07-08 narrative/placement.tex
work in progress....

The application workflows targeted in this proposal generate very large
amounts of data, which needs to be processed and analyzed before
potential insights from the simulations can be realized. 
The overall data life cycle consists of four phases. Data starts
when it is generated by a simulation or through a data acquisition system,
in the case of experimental and observational data (EOD). 
In our target heterogenous multi-tier storage platform, the system must
decide where to place the output data at this time, and how to partition and
reorganize the data to optimize this initial placement. The key optimization
metrics during this phase is the percieved I/O overhead for the application.

In the second phase of the data life cycle, the system takes over the
management of the data and performs the necessary steps to meet service
level objectives (SLOs). These steps include migration, reorganization, and
reductions for the data. During this phase the system optimizes for resource
utilization, interference with running applications, and availability and
resiliency objectives. Data can be moved into archival storage (tape or cold
storage) during this phase.

@@

In the final phase the data is purged from the system altogether. The
decision to purge is made by the system based on operational metrics from
system administrators. This phase optimizes the space available in the
system to prevent out of space concerns for applications.

Our proposed research explores the management of this entire life cycle
given our thesis that more knowledge, and more specific knowledge about the
data, can allow the management of data to be optimized with reduced cost.
Thus, we will explore the following high level research questions: (1) What methods can
be utilized in the initial placement of data that do not impose expensive
costs on discovery, consumption and migration? (2) How can the placement of
data be optimized for the multi-tiered hierarchy expected in exascale
systems? (3) How can we migrate data throughout the layers of storage
without making the discovery process unbounded? (4) How does the additional
knowledge aid in preparing the data for reading in a timely manner? (5) How
do we make the decision on purging using this additional knowledge?

>>>>

The application workflows targeted in this proposal generate very large
amounts of data, which needs to be processed and analyzed before
potential insights from the simulations can be realized. 
The overall data life cycle can be viewed as consisting of four key phases. In the first phase data 
is generated by a simulation or through a data acquisition system,
in the case of experimental and observational data (EOD). This data has 
to be appropriately initially placed (and possibly partitioned) within the heterogenous 
multi-tier storage to optimize application I/O overheads.
%In our proposed heterogenous multi-tier storage platform, the system must
%decide where to place the output data at this time, and how to partition and
%reorganize the data to optimize this initial placement. The key optimization
%metrics during this phase is the perceived I/O overhead for the application.

In the second phase of the data life cycle, the data is managed by the to 
meet application requirements and constraints. This includes migration, 
reorganization and reduction of the data, etc., to optimize resource
utilization, interference with running applications, and availability and
resiliency objectives. 
%Data can be moved into archival storage (tape or cold storage) during this phase. 
%
%In the second phase of the data life cycle the system takes over the
%management of the data and performs the necessary steps to meet service
%level objectives (SLOs). These steps include migration, reorganization, and
%reductions for the data. During this phase the system optimizes for resource
%utilization, interference with running applications, and availability and
%resiliency objectives. Data can be moved into archival storage (tape or cold
%storage) during this phase.

@@

In the final phase the data is purged from the system. The
decision to purge may be made by the system based on operational metrics from
system administrators or by the user. This phase optimizes the space available in the
system. % to prevent out of space concerns for applications.

Our proposed research will address the management of data across the entire life cycle 
in an application driven and system aware manner. 
%given our thesis that more knowledge, and more specific knowledge about the
%data, can allow the management of data to be optimized with reduced cost.
Some of the high level research questions that we will explore are as follows: 
(1) How can we initially place data so that it can be discovered and consumed efficiently?
%What methods can be utilized in the initial placement of data that do not impose expensive
%costs on discovery, consumption and migration? 
(2) How can the placement and migration of data across a multi-tiered storage hierarchy be 
optimized at runtime, both from the application and system perspective?
%(3) How can we migrate data throughout the layers of storage
%without making the discovery process unbounded? 
(4) How can knowledge about the application used to better prepare the data for consumption? 
(5) When and how do we make the decision to purge data?  %using this additional knowledge?
